---
title: "Genre DEMO"
output: html_notebook
---

This is the demo for solve Genre problematic. In order to well understand this file was resumed to only show up the data partition and model test.

Main goal of this model:
- Predict genres based on song features;


Considerations:

- "Others" contains among genres known, anothers genres do not categorized.
- 


```{r}
#Load data
genres = read.csv(file = '~/Documents/dp_datamining/data/dataGenre.csv', header = TRUE, na.strings = "?")

#Data Preparation 
#Remove lyrics from this set
genres$titlesong <- NULL
#Remove "tempo equals 0, because is not relevante for now."
genres <- genres[!genres$tempo <= 45.0 & !genres$tempo >= 250.0,]
#Remove "Others from type of group, because is not relevante now."
genres <- genres[!genres$typegroup == "Others",]

genres$Class[genres$genretype=='Others'] <- 0
genres$Class[genres$genretype=='Rock'] <- 1
genres$Class[genres$genretype=='Pop'] <- 1
genres$Class[genres$genretype=='Hip Hop'] <- 1
genres$Class[genres$genretype=='Jazz'] <- 1
genres$Class[genres$genretype=='Funk'] <- 1
genres$Class[genres$genretype=='Folk'] <- 1
genres$Class[genres$genretype=='Classical'] <- 1
genres$Class[genres$genretype=='Blues'] <- 1
genres$Class[genres$genretype=='Country'] <- 1
genres$Class[genres$genretype=='Electronic'] <- 1

#Create variables of genres
genres$Rock[genres$genretype=='Rock'] <- TRUE
genres$Rock[genres$genretype!='Rock'] <- FALSE

genres$Pop[genres$genretype=='Pop'] <- TRUE
genres$Pop[genres$genretype!='Pop'] <- FALSE

genres$Electronic[genres$genretype=='Electronic'] <- TRUE
genres$Electronic[genres$genretype!='Electronic'] <- FALSE

genres$HipHop[genres$genretype=='Hip Hop'] <- TRUE
genres$HipHop[genres$genretype!='Hip Hop'] <- FALSE

genres$Jazz[genres$genretype=='Jazz'] <- TRUE
genres$Jazz[genres$genretype!='Jazz'] <- FALSE

genres$Funk[genres$genretype=='Funk'] <- TRUE
genres$Funk[genres$genretype!='Funk'] <- FALSE

genres$Folk[genres$genretype=='Folk'] <- TRUE
genres$Folk[genres$genretype!='Folk'] <- FALSE

genres$Classical[genres$genretype=='Classical'] <- TRUE
genres$Classical[genres$genretype!='Classical'] <- FALSE

genres$Country[genres$genretype=='Country'] <- TRUE
genres$Country[genres$genretype!='Country'] <- FALSE

genres$Blues[genres$genretype=='Blues'] <- TRUE
genres$Blues[genres$genretype!='Blues'] <- FALSE



summary(genres$genretype)

summary(genres)
```

Steps to prepare data for the Classfication Model:
1. Reduction of the dataset of "Others" for take a proportion;
2. If necessary viabilization of a set for a 3th test


```{r}
#take a sample of genres "Others"
#Only 2% from attributes with the label Others
idx_others <- genres[sample(which(genres$genretype=='Others'),size = 0.02* nrow(genres[which(genres$genretype=='Others'),]) ), ]
#dataset without the label Others
dataset_withoutOthers <- genres[!genres$genretype=='Others',]
#Reattach A small and random data set with Others
genres_ToSplit <- bind_rows(idx_others,dataset_withoutOthers)

summary(genres_ToSplit)
```



2. Split data in 2 dataset:
2.1 Train
2.2 Test

```{r}
# Split between 80 and 30
index <- sample(1:nrow(genres_ToSplit),size = 0.7* nrow(genres_ToSplit))
# Use the large partition to training - 70
train <- genres_ToSplit[index,]
# Use the small partition to test - 30
test <- genres_ToSplit[-index,]

```


```{r}
summary(train)
```

Build the first classfication model with set of training
```{r}
#Build the first classfication model
#to using the command rpat, R will build a tree where Class is to be predicted from the variable presents at the formula

#Model classfication of train
trainTree_Rock = rpart(Class ~ Rock+tempo+energy+danceability+speechiness+accoustiness+loudness+valence+instrumentalness, data = train, method = "class")

#Plotting the tree of train
plot(trainTree_Rock, compress=TRUE, uniform=TRUE)
text(trainTree_Rock,use.n = T,all=T,cex=.7, pretty=0, xpd=TRUE, digits = 6)
prp(trainTree_Rock, extra=101)
# Visualize the decision tree with rpart.plot
rpart.plot(trainTree_Rock, box.palette="RdBu", shadow.col="gray", nn=TRUE)
#Test errors of train tree
pred <- predict(trainTree_Rock, train, type = "class")
mConfusion <- table(train$Class, pred)
TrainErr <- 1 - (mConfusion[1,1]+mConfusion[2,2])/sum(mConfusion)
print(TrainErr)
#Compute errors
TrainErr5 <- 1 - (mConfusion[1,2]+mConfusion[2,1])/sum(mConfusion)
print(TrainErr5)


```

Build the first classfication model with set of test
```{r}
#Build the first classfication model
#to using the command rpat, R will build a tree where Class is to be predicted from the variable presents at the formula


#Model classfication of train
testTree_Rock = rpart(Class ~ Rock+tempo+energy+danceability+speechiness+accoustiness+loudness+valence+instrumentalness, data = test, method = "class")

#Plotting the tree of train
plot(testTree_Rock, compress=TRUE, uniform=TRUE)
text(testTree_Rock,use.n = T,all=T,cex=.7, pretty=0, xpd=TRUE, digits = 6)
prp(testTree_Rock, extra=101)
# Visualize the decision tree with rpart.plot
rpart.plot(testTree_Rock, box.palette="RdBu", shadow.col="gray", nn=TRUE)
#Test errors of train tree
pred <- predict(testTree_Rock, test, type = "class")
mConfusion <- table(test$Class, pred)
TrainErr <- 1 - (mConfusion[1,1]+mConfusion[2,2])/sum(mConfusion)
print(TrainErr)
#Compute errors
TrainErr5 <- 1 - (mConfusion[1,2]+mConfusion[2,1])/sum(mConfusion)
print(TrainErr5)

```


