---
title: "Genre DEMO:SVM Radial"
output: html_notebook
---

This is the demo for solve Genre problematic. In order to well understand it, this file was resumed to only show up the data partition and model test.

About this set:
- Multi class only genres known;
- "Others" contains among genres known, anothers genres that were not categorized.
- Rock are songs that contains the aggretion of subgenre of Rock;
- The data has not discretes values;
- tempo, energy, danceability, etc are song features;
- Duration is not take in consideration on thoses models;
- We use 2% of Others, because it has 40k of songs. Thus we choose reduce others class.
- We are using for test and train datasets random proportional partitions;

Strategies:
- Supervised Classification;

Considerations:
- test set has a size of 30%;
- train set has a size of 70%;

Models:
- SVM Radial;
- SVM Linear;
- KNN;
- Naive Bayne;

Main goal of the best model:
- Classify/Predict new instances using these models;
- Find the must importance features;
- Find the best model possible;


```{r}
library(dplyr)
library(quadprog)
library(sjlabelled)


allGenres = read.csv(file = '~/Documents/dp_datamining/data/allGenresV2.csv', sep = ";", header = TRUE, na.strings = "?")
othersG = read.csv(file = '~/Documents/dp_datamining/data/dataGenre.csv', header = TRUE, na.strings = "?")




#Remove "tempo equals 0, because is not relevante for now."
allGenres <- allGenres[!allGenres$tempo <= 45.0 & !allGenres$tempo >= 250.0,]
othersG <- othersG[!othersG$tempo <= 45.0 & !othersG$tempo >= 250.0,]
#Remove column from this set
allGenres$titlesong <- NULL
allGenres$typegroup <- NULL

othersG$titlesong <- NULL
othersG$typegroup <- NULL
#Pick only Others
othersG <- othersG[ sample( which(othersG$genretype== "Others"), round(0.02*length(which(othersG$genretype== "Others")))), ]
othersG <- othersG[which(!othersG$genretype=='NA'),]


summary(allGenres$genretype)
summary(allGenres)
summary(othersG)
summary(othersG$genretype)

```

```{r}
library(caret)

# # Split between 80 and 30
# #index_Rock <- sample(1:nrow(rock_df),size = 0.7* nrow(rock_df))
# index_allGenre <- createDataPartition(y = allGenres$genretype, p= 0.7, list = FALSE)
# # Use the large partition to training - 70
# train_allGenre <- allGenres[index_allGenre,]
# # Use the small partition to test - 30
# test_allGenre <- allGenres[-index_allGenre,]
# 
# #train_allGenre <- train_allGenre[which(!train_allGenre$genretype=='NA'),]
# str(train_allGenre)
# summary(train_allGenre)
# str(train_allGenre)
# class(train_allGenre)
# 
# #test_allGenre <- test_allGenre[which(!test_allGenre$genretype=='NA'),]
# str(test_allGenre)
# summary(test_allGenre)
# str(test_allGenre)
# class(test_allGenre)


library("splitstackshape")
test<-stratified(allGenres,"genretype", size=.3)

train_allGenre<-setdiff(allGenres,test)
train_allGenre <- train_allGenre[which(!train_allGenre$genretype=='NA'),]
summary(train_allGenre)
summary(train_allGenre$genretype)

test_allGenre <- test[which(!test$genretype=='NA'),]
summary(test_allGenre)
```

```{r}
library(caret)
library(lattice)
library(ggplot2)
library(caret)
library(klaR)
library(MASS)

# Run algorithms using 10-fold cross validation
control <- trainControl(method="cv", number=10)
metric <- "Accuracy"

#+tempo+energy+danceability+speechiness+accoustiness+loudness+duration+valence+instrumentalness
formula_SVM <- genretype~ +tempo+energy+danceability+speechiness+accoustiness+loudness-duration+valence+instrumentalness


#SVM Radial 
# grid_radial <- expand.grid(sigma = c(0,
#  0.05,0.1, 0.25, 0.5, 0.75,0.9),
#  C = c(0,0.01, 0.05, 0.1, 0.25, 0.5, 0.75,
#  1, 1.5, 2,5))

set.seed(3233)
controlGrid <- trainControl(method="cv", number=10)
svm_Radial_Grid <- train(genretype ~.,
                         data = train_allGenre,
                         method = "svmRadial",
                         trControl=controlGrid,
                         preProcess = c("center", "scale"),
                         #tuneGrid = grid_radial,
                         tuneLength = 10)

svm_Radial_Grid
plot(svm_Radial_Grid)
#plot(svm_Radial_Grid, train_Rock2)
```
```{r}
predRadial <- predict(svm_Radial_Grid, newdata = test_allGenre)
#Confusion Matrix and Statistics
confusionMatrix(predRadial, test_allGenre$genretype )

```

```{r}
predRadial <- predict(svm_Radial_Grid, newdata = othersG)
#Confusion Matrix and Statistics
confusionMatrix(predRadial, othersG$genretype )
```

