---
title: "Genre DEMO:SVM Radial OneVsOne"
output: html_notebook
---

This is the demo for solve Genre problematic. In order to well understand it, this file was resumed to only show up the data partition and model test.

About this set:
- Two class, Others and Rock;
- "Others" contains among genres known, anothers genres that were not categorized.
- Rock are songs that contains the aggretion of subgenre of Rock;
- The data has not discretes values;
- tempo, energy, danceability, etc are song features;
- Duration is not take in consideration on thoses models;
- We use 2% of Others, because it has 40k of songs. Thus we choose reduce others class.
- We are using for test and train datasets random proportional partitions;

Considerations:
- test set has a size of 30%;
- train set has a size of 70%;

Strategies:
- One vs One;
- Supervised Classification;

Models:
- SVM Radial;
- SVM Linear;
- KNN;
- Naive Bayne;

Main goal of the best model:
- Classify/Predict new instances using these models;
- Find the must importance features;
- Find the best model possible;


Vocabulary:

"discrete values" : ( Binary values like 0/1, yes/no, true/false )

'formula' : 

The variable on the left-hand side of a tilde (~) is called the "dependent variable"("response variable", "outcome variable" or "label"), while the variables on the right-hand side are called the "independent variables" ("predictor (variable)", "controlled variable", "feature") and are joined by plus signs +.

"+" : for adding terms;
"-" : for removing terms;



References:

Music Map:
https://musicmap.info/

Classification of Artist Genre through Supervised Learning
http://cs229.stanford.edu/proj2016/report/RidleyDumovic-ClassificationOfArtistGenrethroughSupervisedLearning-report.pdf?fbclid=IwAR2WJEi8JdE2Ut_xwUe0WWZPFJUBxm16UE9vpkrXlnCF23Edeu2SMwzTQgU

SUPPORT VECTOR MACHINE CLASSIFIER IMPLEMENTATION IN R WITH CARET PACKAGE
http://dataaspirant.com/2017/01/19/support-vector-machine-classifier-implementation-r-caret-package/


http://cs229.stanford.edu/proj2016/report/RidleyDumovic-ClassificationOfArtistGenrethroughSupervisedLearning-report.pdf?fbclid=IwAR2WJEi8JdE2Ut_xwUe0WWZPFJUBxm16UE9vpkrXlnCF23Edeu2SMwzTQgU
```{r}
library(dplyr)
library(quadprog)
library(sjlabelled)
#Load data
#genres = read.csv(file = '~/Documents/dp_datamining/data/dataGenre.csv', header = TRUE, na.strings = "?")

rockG = read.csv(file = '~/Documents/dp_datamining/data/rockG.csv', sep = ";", header = TRUE, na.strings = "?")
#popG = read.csv(file = '~/Documents/dp_datamining/data/popG.csv', sep = ";", header = TRUE, na.strings = "?")
#electronicG = read.csv(file = '~/Documents/dp_datamining/data/electronicG.csv', sep = ";", header = TRUE, na.strings = "?")
othersG = read.csv(file = '~/Documents/dp_datamining/data/othersG.csv', sep = ";", header = TRUE, na.strings = "?")

#Remove "tempo equals 0, because is not relevante for now."
rockG <- rockG[!rockG$tempo <= 45.0 & !rockG$tempo >= 250.0,]
#Remove column from this set
rockG$titlesong <- NULL
rockG$typegroup <- NULL
#rockG$duration <- NULL
#rockG$loudness <- NULL
#ockG$accoustiness <- NULL
#rockG$energy <- NULL
# rockG$Class[rockG$energy < 0.8] <- 0
# rockG$Class[rockG$energy >= 0.8] <- 1

#take a sample of genres "Others"
#Only 1% from attributes with the label Others
others_df <- rockG[ sample( which(rockG$genretype== "Others"), round(0.02*length(which(rockG$genretype== "Others")))), ]

rock_df <- rockG[which(rockG$genretype=='Rock'),]
#Reattach A small and random data set with Others
rock_df <- bind_rows(others_df,rock_df)


summary(rock_df)
str(rock_df)
class(rock_df)




#summary(others_df)
# summary(rockG)
# class(rockG)


#Reattach A small and random data set with Others
#rock_df <- bind_rows(rockG,others_df)
#rock_df <- data.frame(others_df,rockG)
#summary(rock_df$genretype)


# #Data Preparation 
# #Remove lyrics from this set
# #genres$titlesong <- NULL
# #Remove "tempo equals 0, because is not relevante for now."
# genres <- genres[!genres$tempo <= 45.0 & !genres$tempo >= 250.0,]
# #Remove "Others from type of group, because is not relevante now."
# genres <- genres[!genres$typegroup == "Others",]
# genres$titlesong <- NULL
# genres$typegroup <- NULL
# 
# #genres$Category[genres$genretype=='Others'] <- 0
# #genres$Category[genres$genretype=='Rock'] <- 1
# 
# rock_df <-genres[which(genres$genretype=='Rock'),] # genres[is.element(genres$genretype,'Rock' ),] filter(genres, genres$genretype %in% 'Rock') #
# 
# 
# 
# 
# 
# 
# 
# pop_df <- genres[which(genres$genretype=='Pop'),]
# Electronic_df <- genres[which(genres$genretype=='Electronic'),]



#take a sample of genres "Others"
#Only 2% from attributes with the label Others
#others_df <- genres[sample(which(genres$genretype=='Others'),size = 0.02* nrow(genres[which(genres$genretype=='Others'),]) ), ]

#others_df$genretype<-factor(others_df$genretype)
#others_df <- droplevels(others_df)

#dataset without the label Others
#For any case
# dataset_withoutOthers <- genres[!genres$genretype=='Others',]
# summary(dataset_withoutOthers$genretype)


# #Reattach A small and random data set with Others
# rock_df <- bind_rows(others_df,rock_df)
# #rock_df <- remove_labels(rock_df$genretype, labels = 'Blues')
# 
# rock_df <- droplevels(rock_df)
# rock_df <- transform(rock_df, genretype = factor(genretype, labels = "Rock"))
# rock_df <- subset(rock_df, genretype != "Rock")
# table(rock_df$genretype)
# table(droplevels(rock_df)$genretype)
# 

#1: Others
#2: Rock

#summary(rock_df$genretype)
#print(rock_df)


```


```{r}
library(caret)
library(lattice)
library(ggplot2)
# #One vs One: Rock
# # Split between 80 and 30
# #index_Rock <- sample(1:nrow(rock_df),size = 0.7* nrow(rock_df))
# index_Rock <- createDataPartition(y = rock_df$genretype, p= 0.7, list = FALSE)
# # Use the large partition to training - 70
# train_Rock <- rock_df[index_Rock,]
# # Use the small partition to test - 30
# test_Rock <- rock_df[-index_Rock,]
# 
# train_Rock <- train_Rock[which(!train_Rock$genretype=='NA'),]
# str(train_Rock)
# summary(train_Rock)
# str(train_Rock)
# class(train_Rock)
# 
# test_Rock <- test_Rock[which(!test_Rock$genretype=='NA'),]
# str(test_Rock)
# summary(test_Rock)
# str(test_Rock)
# class(test_Rock)


library("splitstackshape")
test<-stratified(rock_df,"genretype", size=.3)

train_Rock<-setdiff(rock_df,test)
train_Rock <- train_Rock[which(!train_Rock$genretype=='NA'),]
summary(train_Rock)
summary(train_Rock$genretype)

test_Rock <- test[which(!test$genretype=='NA'),]
summary(test_Rock)



```


```{r}
library(caret)
library(lattice)
library(ggplot2)
library(klaR)
library(MASS)

# Run algorithms using 10-fold cross validation
control <- trainControl(method="cv", number=10)
metric <- "Accuracy"

#+tempo+energy+danceability+speechiness+accoustiness+loudness+duration+valence+instrumentalness
formula_SVM <- genretype~ .


#SVM Linear 
set.seed(89)
fit.svmLinear_train <- train(formula_SVM,
                             data = train_Rock,
                             method = "svmLinear",
                             trControl=control,
                             preProcess = c("center", "scale"),
                             tuneLength = 10)
fit.svmLinear_train
#plot(fit.svmLinear_train)

#SVM Radial 
set.seed(89)
fit.svmRadial_train <- train(formula_SVM,
                             data = train_Rock,
                             method = "svmRadial",
                             trControl=control,
                             preProcess = c("center", "scale"),
                             tuneLength = 10)
fit.svmRadial_train
#plot(fit.svmRadial_train)

#KNN 
set.seed(89)
fit.knn_train <- train(formula_SVM,
                             data = train_Rock,
                             method = "knn",
                             trControl=control,
                             preProcess = c("center", "scale"),
                             tuneLength = 10)
fit.knn_train
#plot(fit.knn_train)

#NaiveBayne 
set.seed(89)
fit.nb_train <- train(formula_SVM,
                             data = train_Rock,
                             method = "nb",
                             trControl=control,
                             preProcess = c("center", "scale"),
                             tuneLength = 10)
fit.nb_train
#plot(fit.nb_train)


# summarize accuracy of models
results <- resamples(list(svmLinear=fit.svmLinear_train,
                          #mxnet=fit.mxnet_train,
                          nb=fit.nb_train, 
                          knn=fit.knn_train,
                          svmRadial=fit.svmRadial_train))
summary(results)

# compare accuracy of models
dotplot(results)

```
```{r}
# estimate variable importance
importance <- varImp(fit.svmRadial_train, scale=FALSE)
# summarize importance
print(importance)
# plot importance
plot(importance)
```


```{r}
library(MASS)
library(plot3D)
#Choose the best model
bestModel <- fit.svmRadial_train

test_pred <- predict(bestModel, newdata = test_Rock)
confusionMatrix(test_pred, test_Rock$genretype )
#plot(bestModel,
     #plotType = "line",
     #metric = "Accuracy"
     #digits = getOption("digits") - 3,
     #xTrans = NULL,
     #nameInStrip = FALSE, ...
     #)



p=ggplot(test_Rock,
         aes(y=test_Rock$energy,
             x=test_Rock$accoustiness,
             color=test_Rock$genretype ))
p+geom_point(size=2)

p=ggplot(test_Rock,
         aes(y=test_Rock$energy,
             x=test_Rock$loudness,
             color=test_Rock$genretype ))
p+geom_point(size=2)



summary(test_Rock$genretype)
my_cols <- c("#FC4E07","#00AFBB")  
pairs(test_Rock[,2:9], pch = 20,  cex = 0.1,
      col = my_cols[test_Rock$genretype],
      lower.panel=NULL)
```

```{r}
#Trying predict what song in other maybe is Rock
summary(others_df$genretype)
test_pred <- predict(fit.svmRadial_train, newdata = others_df)
confusionMatrix(test_pred,others_df$genretype )
```

```{r}
#Trying to predict what song in other maybe is Rock. Doing that with a dataset of 50% others.
others_df2 <- rockG[ sample( which(rockG$genretype== "Others"), round(0.5*length(which(rockG$genretype== "Others")))), ]
others_df2$titlesong <- NULL
others_df2$typegroup <- NULL


#Reattach A small and random data set with Others
tes_df2 <- bind_rows(others_df,rockG[which(rockG$genretype=='Rock'),])


str(tes_df2)
summary(tes_df2$genretype)

#Then to double check, we create a second set that containts others and rock genre.
othersG_pred <- predict(fit.svmRadial_train, newdata = tes_df2)
confusionMatrix(othersG_pred, tes_df2$genretype )
```


