---
title: "Genre DEMO:SVM Radial"
output: html_notebook
---

This is the demo for solve Genre problematic. In order to well understand it, this file was resumed to only show up the data partition and model test.

About this set:
- Multi labels;
- Not discrete values;
- 


Main goal of this model:
- Classify new instances using these models;

Strategies:
- Find the must importantes features;
- Find the best model possible;
- Apply Supervised Classi fication;


Considerations:

- "Others" contains among genres known, anothers genres do not categorized.
- 


Vocabulary:

"discrete values" : ( Binary values like 0/1, yes/no, true/false )

'formula' : 

The variable on the left-hand side of a tilde (~) is called the "dependent variable"("response variable", "outcome variable" or "label"), while the variables on the right-hand side are called the "independent variables" ("predictor (variable)", "controlled variable", "feature") and are joined by plus signs +.

"+" : for adding terms;
"-" : for removing terms;



References:

Music Map:
https://musicmap.info/

Classification of Artist Genre through Supervised Learning
http://cs229.stanford.edu/proj2016/report/RidleyDumovic-ClassificationOfArtistGenrethroughSupervisedLearning-report.pdf?fbclid=IwAR2WJEi8JdE2Ut_xwUe0WWZPFJUBxm16UE9vpkrXlnCF23Edeu2SMwzTQgU
```{r}
library(dplyr)
library(quadprog)
library(sjlabelled)
#Load data
#genres = read.csv(file = '~/Documents/dp_datamining/data/dataGenre.csv', header = TRUE, na.strings = "?")

rockG = read.csv(file = '~/Documents/dp_datamining/data/rockG.csv', sep = ";", header = TRUE, na.strings = "?")
#popG = read.csv(file = '~/Documents/dp_datamining/data/popG.csv', sep = ";", header = TRUE, na.strings = "?")
#electronicG = read.csv(file = '~/Documents/dp_datamining/data/electronicG.csv', sep = ";", header = TRUE, na.strings = "?")
othersG = read.csv(file = '~/Documents/dp_datamining/data/othersG.csv', sep = ";", header = TRUE, na.strings = "?")

#Remove "tempo equals 0, because is not relevante for now."
rockG <- rockG[!rockG$tempo <= 45.0 & !rockG$tempo >= 250.0,]
#Remove column from this set
rockG$titlesong <- NULL
rockG$typegroup <- NULL
# rockG$Class[rockG$genretype=='Others'] <- 0
# rockG$Class[rockG$genretype=='Rock'] <- 1

#take a sample of genres "Others"
#Only 1% from attributes with the label Others
others_df <- rockG[ sample( which(rockG$genretype== "Others"), round(0.01*length(which(rockG$genretype== "Others")))), ]

rock_df <- rockG[which(rockG$genretype=='Rock'),]
#Reattach A small and random data set with Others
rock_df <- bind_rows(others_df,rock_df)


summary(rock_df)
str(rock_df)
class(rock_df)




#summary(others_df)
# summary(rockG)
# class(rockG)


#Reattach A small and random data set with Others
#rock_df <- bind_rows(rockG,others_df)
#rock_df <- data.frame(others_df,rockG)
#summary(rock_df$genretype)


# #Data Preparation 
# #Remove lyrics from this set
# #genres$titlesong <- NULL
# #Remove "tempo equals 0, because is not relevante for now."
# genres <- genres[!genres$tempo <= 45.0 & !genres$tempo >= 250.0,]
# #Remove "Others from type of group, because is not relevante now."
# genres <- genres[!genres$typegroup == "Others",]
# genres$titlesong <- NULL
# genres$typegroup <- NULL
# 
# #genres$Category[genres$genretype=='Others'] <- 0
# #genres$Category[genres$genretype=='Rock'] <- 1
# 
# rock_df <-genres[which(genres$genretype=='Rock'),] # genres[is.element(genres$genretype,'Rock' ),] filter(genres, genres$genretype %in% 'Rock') #
# 
# 
# 
# 
# 
# 
# 
# pop_df <- genres[which(genres$genretype=='Pop'),]
# Electronic_df <- genres[which(genres$genretype=='Electronic'),]



#take a sample of genres "Others"
#Only 2% from attributes with the label Others
#others_df <- genres[sample(which(genres$genretype=='Others'),size = 0.02* nrow(genres[which(genres$genretype=='Others'),]) ), ]

#others_df$genretype<-factor(others_df$genretype)
#others_df <- droplevels(others_df)

#dataset without the label Others
#For any case
# dataset_withoutOthers <- genres[!genres$genretype=='Others',]
# summary(dataset_withoutOthers$genretype)


# #Reattach A small and random data set with Others
# rock_df <- bind_rows(others_df,rock_df)
# #rock_df <- remove_labels(rock_df$genretype, labels = 'Blues')
# 
# rock_df <- droplevels(rock_df)
# rock_df <- transform(rock_df, genretype = factor(genretype, labels = "Rock"))
# rock_df <- subset(rock_df, genretype != "Rock")
# table(rock_df$genretype)
# table(droplevels(rock_df)$genretype)
# 

#1: Others
#2: Rock

#summary(rock_df$genretype)
#print(rock_df)


```


```{r}
library(caret)
#One vs One: Rock
# Split between 80 and 30
#index_Rock <- sample(1:nrow(rock_df),size = 0.7* nrow(rock_df))
index_Rock <- createDataPartition(y = rock_df$genretype, p= 0.7, list = FALSE)
# Use the large partition to training - 70
train_Rock <- rock_df[index_Rock,]
# Use the small partition to test - 30
test_Rock <- rock_df[-index_Rock,]

train_Rock <- train_Rock[which(!train_Rock$genretype=='NA'),]
str(train_Rock)
summary(train_Rock)
str(train_Rock)
class(train_Rock)

test_Rock <- test_Rock[which(!test_Rock$genretype=='NA'),]
str(test_Rock)
summary(test_Rock)
str(test_Rock)
class(test_Rock)



```




```{r}
summary(train_Rock)
```






```{r}
library(caret)
library(lattice)
library(ggplot2)
library(caret)
library(klaR)
library(MASS)

# Run algorithms using 10-fold cross validation
control <- trainControl(method="cv", number=10)
metric <- "Accuracy"

#+tempo+energy+danceability+speechiness+accoustiness+loudness+duration+valence+instrumentalness
formula_SVM <- genretype~ .


#SVM Radial 
set.seed(89)
fit.svmRadial_train <- train(formula_SVM,
                             data = train_Rock,
                             method = "svmRadial",
                             trControl=control,
                             preProcess = c("center", "scale"),
                             tuneLength = 10)
fit.svmRadial_train
#plot(fit.svmRadial_train)

```

```{r}
test_pred <- predict(fit.svmRadial_train, newdata = test_Rock)
confusionMatrix(test_pred, test_Rock$genretype )
```

```{r}
summary(others_df$genretype)
test_pred <- predict(fit.svmRadial_train, newdata = others_df)
confusionMatrix(test_pred, others_df$genretype )
```

```{r}

others_df2 <- rockG[ sample( which(rockG$genretype== "Others"), round(0.5*length(which(rockG$genretype== "Others")))), ]
others_df2$titlesong <- NULL
others_df2$typegroup <- NULL

#Reattach A small and random data set with Others
tes_df2 <- bind_rows(others_df,rockG[which(rockG$genretype=='Rock'),])


str(tes_df2)
summary(tes_df2$genretype)

othersG_pred <- predict(fit.svmRadial_train, newdata = tes_df2)
confusionMatrix(othersG_pred, tes_df2$genretype )
```

```{r}
library(caret)
#One vs One: Rock
# Split between 80 and 30
#index_Rock <- sample(1:nrow(rock_df),size = 0.7* nrow(rock_df))
index_Rock2 <- createDataPartition(y = rock_df$genretype, p= 0.7, list = FALSE)
# Use the large partition to training - 70
train_Rock2 <- rock_df[index_Rock2,]
# Use the small partition to test - 30
test_Rock2 <- rock_df[-index_Rock2,]

train_Rock2 <- train_Rock2[which(!train_Rock2$genretype=='NA'),]
# str(train_Rock2)
# summary(train_Rock2)
# str(train_Rock2)
# class(train_Rock2)

test_Rock2 <- test_Rock[which(!test_Rock2$genretype=='NA'),]
# str(test_Rock2)
# summary(test_Rock2)
# str(test_Rock2)
# class(test_Rock2)

grid_radial <- expand.grid(sigma = c(0,
 0.05,0.1, 0.25, 0.5, 0.75,0.9),
 C = c(0,0.01, 0.05, 0.1, 0.25, 0.5, 0.75,
 1, 1.5, 2,5))

set.seed(3233)
controlGrid <- trainControl(method="cv", number=10)
svm_Radial_Grid <- train(genretype ~.,
                         data = train_Rock2,
                         method = "svmRadial",
                         trControl=controlGrid,
                         preProcess = c("center", "scale"),
                         tuneGrid = grid_radial,
                         tuneLength = 10)

svm_Radial_Grid
plot(svm_Radial_Grid)
#plot(svm_Radial_Grid, train_Rock2)
```

```{r}
test_pred_Radial_Grid <- predict(svm_Radial_Grid, newdata = test_Rock2)

confusionMatrix(test_pred_Radial_Grid, test_Rock2$genretype )
#Confusion Matrix and Statistics
```

